Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-05-10 Paper.tex
EIP86: when CREATE(2) destination is occupied, the return value is zero

&&&& $Z(\boldsymbol{\sigma}^*, \boldsymbol{\mu}, I) = \top$ or $I_e = 1024$ \\

@@

&&&& halting $Z(\boldsymbol{\sigma}^*,\boldsymbol{\mu}, I) = \top$ or $I_e = 1024$ (the maximum call depth limit is reached) or \\

>>>>

&&&& $Z(\boldsymbol{\sigma}^*, \boldsymbol{\mu}, I) = \top$, $E(\boldsymbol{\sigma}^*, a) = \top$ (the address is occupied) or $I_e = 1024$ \\

@@

&&&& halting $Z(\boldsymbol{\sigma}^*,\boldsymbol{\mu}, I) = \top$, $E(\boldsymbol{\sigma}, a) = \top$ (the address is already occupied) or \\
&&&& $I_e = 1024$ (the maximum call depth limit is reached), \\
